Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-05 Draft/Draft.Rmd
Parragraph for figure 5

---
title: Plant-pollintor networks worldwide are composed by the same specific building
  blocks
editor_options:
  chunk_output_type: console
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{caption,setspace}
- \captionsetup[figure]{labelformat=empty}
- \floatplacement{figure}{H}
- \usepackage[skip=3pt]{caption}
- \captionsetup[figure]{labelformat=empty}

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE}
##############################
#TABLE S1. List of studies
##############################

@@

references %>%
  arrange(`First author`)%>%
  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
  kable_styling(latex_options = c("repeat_header","striped"), font_size = 12, full_width=T,position = c("center"))

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=12, fig.width=12}

@@

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S2.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
kable_styling(full_width = T) %>%
add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.cap="**Figure S1.** Comparison of the motif frequencies between empirical and simulated networks excluding singletones. Average percentages of motifs close to 0 and 100 indicate under- and over- representation in empirical networks, after removing non-robust links, that is, interactions whose frequency was equal to one. The different motifs are coloured by the mean path length as done in @simmons2020.", fig.width=4.5,fig.height=6.5}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions excluding singletones, after removing non-robust links, that is, interactions whose frequency was equal to one. The different motif positions are dividied by the average path length clasification by @simmons2020."}

@@

@@

>>>>

---
title: Plant-pollintor networks worldwide are composed by the same specific building
  blocks
editor_options:
  chunk_output_type: console
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{caption,setspace}
- \captionsetup[figure]{labelformat=empty}
- \floatplacement{figure}{H}
- \usepackage[skip=3pt]{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{lscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}

@@

The statistical comparison with z-scores between the observed functional group combinations and the expected ones showed a Gausian distribution with 65% of under-represented group combinations, 20% of no statistical difference and 15% of under-represented ones (**Figure 5**). Remarkably, motifs with small node combinations (i.e., 2 and 3 nodes) only appeared as under-represented. Motifs with 4 and 5 node combinations appeared in the three statistical categories but 4 node motifs had a higher porportion in the under-represented category (10% in comparison with the 1% and the 3% of the no statiscal difference and over-represented categories, respectively). Finally, 5 node motifs were in similar prportions in the no statistical difference and over-represented categories (99% and 97%, respectively) but they appeared in lower porportion in the under-represented category (89%). When, we explore the identity on the different positions of the most probable motif combinations we find as expected that the most common functional groups rule these positions on the most probable motif combiantions (lower panel **Figure 5**).

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,fig.width=12,  warning=FALSE}
##############################
#TABLE S1. List of studies
##############################

@@

references %>%
  arrange(`First author`)%>%
  kable( longtable = T, booktabs = T,linesep = "\\addlinespace",align = c("cccc"),escape = FALSE, caption= "\\textbf{Table S1.} List of studies ordered by author with the year of publication, number of contributed networks and digital object identifier") %>%
  kable_styling(latex_options = c("repeat_header","striped"),  full_width=F,position = c("center"))

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, fig.height=16, fig.width=12}

@@

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S2.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
kable_styling(full_width = T,latex_options = c("striped")) %>%
add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S1.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al. (2020) without considering singletones. This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S2.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions excluding singletones, after removing non-robust links, that is, interactions whose frequency was equal to one. The different motif positions are dividied by the average path length clasification by Simmons et al. (2020)"}

@@

\blandscape

@@

\elandscape
